WSClean: an implementation of a fast, generic wide-field imager

### 2014-03-01 articles/2014/Article-WSClean/wsclean.tex
Comment Ord

Another option exists for imaging MWA data: the Real-Time System (RTS, \citealt{rts-mwa}). This has been designed as an efficient calibration and imaging pipeline specifically for MWA data. It can use GPUs to improve efficiency, and uses a $w$-projection kernel during imaging to correct for the $w$-term. The kernel can be kept small, because the data is processed in snapshots. The RTS can not perform deconvolution as of yet.

>>>>

Another option exists for imaging MWA data: the Real-Time System (RTS, \citealt{rts-mwa,mwa-interferometric-imaging}). This has been designed as an efficient calibration and imaging pipeline specifically for MWA data. It can use GPUs to improve efficiency. It performs snapshot imaging to deal with the $w$-term, which implies that slight variations in tile elevation cause some decorrelation on the longer baselines. The RTS can not perform deconvolution as of yet.
